Using DIT to simplify the DBF feasibility test

### 2013-07-19 dit-paper.tex
fixed multi-cite and dbf t_1 t_2 sum formula

\begin{definition}
 The \textbf{demand-bound function (DBF)} (\cite{baruah1999generalized} and \cite{baruah1990algorithms}), defined for a task set $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\

 Mathematically,
 $$\dbf{t} = \max_{\{t_1, t_2 \; : \; t_2 - t_1 = t\}} \sum_{i=1}^n C_i \; h_i(t_1, t_2)$$
 where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
\end{definition}

>>>>

\begin{definition}
 The \textbf{demand-bound function (DBF)}
 \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
 $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\

 Mathematically,
 $$\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
 \leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2)$$ where
 $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
\end{definition}
